A Triple Origin for Twin Blue Stragglers in Compact Binaries

### 2018-12-29 BSS7782.tex
included apj.bst and corrected few minor typos

For V4046 Sgr, for which the two stars have comparable masses as in
our calculation in an ciruclar orbit with a period of only 2.4 days
they find that the inner binary accretes at a rate of $\sim
0.028$\,\MSun/Myr.  For DQ~Tau, which is composed of lower-mass stars
($m_1 = m_2 \seimq 0.55$\,\MSun) in an eccentric ($e\simeq 0.556$)
orbit of $\sim 15.8$\,days they find an accretion rate onto the inner
binary of $\sim 0.027$\,\MSun/Myr.  These values are in the same range
as in our calculations, which results in an accretion rate of the inner
binary of 0.027--0.058\,\MSun/Myr (i.e., the average measured over a period of
about 3000 days in our simulations).  The highest accretion rate we obtain for the
simulations with an eccentric inner orbit.  Here we applied a small
correction to compensate for the larger accretion radii adopted for
the two stars of 10\,\RSun\, compared to 6\,\RSun\, in
\cite{2011MNRAS.413.2679D}. Interestingly, however,
\cite{2011MNRAS.413.2679D} find that the primary star in V4046 Sgr
accretes at an 8\% higher rate than the secondary star, whereas in our
case the secondary star accretes at a higher rate than the primary
star by about 1\% to 12\%.  Higher accretion rates in the secondary
star are realized for eccentric and retrogade inner orbits.
%NL2:  Huh.  This is interesting.  Is the physical reason for it that apocenter for the secondary tends to be closer to the circumbinary disk?  I don't get why retrograde wins though, since naively I'd have thought prograde should lead to lower relative velocities between the secondary and the gas flow, and hence to higher accretion rates.  What am I missing?  Is there momentum cancellation via colliding gas, shocks, etc. I am missing somewhere?

@@

\bibliographystyle{apj}
\bibliography{BBS7782}

>>>>

For V4046 Sgr, for which the two stars have comparable masses as in
our calculation in an ciruclar orbit with a period of only 2.4 days
they find that the inner binary accretes at a rate of $\sim
0.028$\,\MSun/Myr.  For DQ~Tau, which is composed of lower-mass stars
($m_1 = m_2 \simeq 0.55$\,\MSun) in an eccentric ($e\simeq 0.556$)
orbit of $\sim 15.8$\,days they find an accretion rate onto the inner
binary of $\sim 0.027$\,\MSun/Myr.  These values are in the same range
as in our calculations, which results in an accretion rate of the inner
binary of 0.027--0.058\,\MSun/Myr (i.e., the average measured over a period of
about 3000 days in our simulations).  The highest accretion rate we obtain for the
simulations with an eccentric inner orbit.  Here we applied a small
correction to compensate for the larger accretion radii adopted for
the two stars of 10\,\RSun\, compared to 6\,\RSun\, in
\cite{2011MNRAS.413.2679D}. Interestingly, however,
\cite{2011MNRAS.413.2679D} find that the primary star in V4046 Sgr
accretes at an 8\% higher rate than the secondary star, whereas in our
case the secondary star accretes at a higher rate than the primary
star by about 1\% to 12\%.  Higher accretion rates in the secondary
star are realized for eccentric and retrogade inner orbits.
%NL2:  Huh.  This is interesting.  Is the physical reason for it that apocenter for the secondary tends to be closer to the circumbinary disk?  I don't get why retrograde wins though, since naively I'd have thought prograde should lead to lower relative velocities between the secondary and the gas flow, and hence to higher accretion rates.  What am I missing?  Is there momentum cancellation via colliding gas, shocks, etc. I am missing somewhere?

@@

\bibliographystyle{apj}
\bibliography{BSS7782}
